---
title: "Mini Data-Analysis Deliverable 1"
output: github_document
always_allow_html: yes
---

## Data Installation

1.  Install the [`datateachr`](https://github.com/UBC-MDS/datateachr) package by typing the following into your **R terminal**:

<!-- -->

    install.packages("devtools")
    devtools::install_github("UBC-MDS/datateachr")


2.  Load the packages below.

```{r}
library(datateachr) # --> for loading dataset for this work
library(tidyverse) # --> for data wrangling and analysis
library(naniar) # --> for missing data analysis
library(ggridges) # --> for distribution plots
library(ggpubr) # --> for better plotting (uses ggplot2)
library(scales) # --> for scaling data
library(kableExtra) # --> for pretty table printing
```
## Learning Objectives

By the end of this milestone, you should:

-   Become familiar with your dataset of choosing
-   Select 4 questions that you would like to answer with your data
-   Generate a reproducible and clear report using R Markdown
-   Become familiar with manipulating and summarizing your data in tibbles using `dplyr`, with a research question in mind.

-----
# Milestone 1


## Task 1: Choose your favorite dataset (10 points)

The `datateachr` package by Hayley Boyce and Jordan Bourak currently composed of 7 semi-tidy datasets for educational purposes. Here is a brief description of each dataset:

-   *apt_buildings*: Acquired courtesy of The City of Toronto's Open Data Portal. It currently has 3455 rows and 37 columns.

-   *building_permits*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 20680 rows and 14 columns.

-   *cancer_sample*: Acquired courtesy of UCI Machine Learning Repository. It currently has 569 rows and 32 columns.

-   *flow_sample*: Acquired courtesy of The Government of Canada's Historical Hydrometric Database. It currently has 218 rows and 7 columns.

-   *parking_meters*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 10032 rows and 22 columns.

-   *steam_games*: Acquired courtesy of Kaggle. It currently has 40833 rows and 21 columns.

-   *vancouver_trees*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 146611 rows and 20 columns.


1.1 Out of the 7 datasets available in the `datateachr` package, choose **4** that appeal to you based on their description. Write your choices below:



<!-------------------------- Start your work below ---------------------------->

* 1: **CHOICE_1**: parking_meters
* 2: **CHOICE_2**: vancouver_trees
* 3: **CHOICE_3**: apt_buildings
* 4: **CHOICE_4**: building_permits

<!----------------------------------------------------------------------------->


1.2 One way to narrowing down your selection is to *explore* the datasets. Use your knowledge of dplyr to find out at least *3* attributes about each of these datasets (an attribute is something such as number of rows, variables, class type...). The goal here is to have an idea of *what the data looks like*.

*Hint:* This is one of those times when you should think about the cleanliness of your analysis. I added a single code chunk for you below, but do you want to use more than one? Would you like to write more comments outside of the code chunk?

<!-------------------------- Start your work below ---------------------------->

### Exploring "parking_meters"
```{r}
### EXPLORE HERE ###
str(parking_meters)

# Type of meter_head and their counts
parking_meters %>% group_by(meter_head) %>% 
  summarise(count = n())

```

**Comments**

1. Data has multiple string entries
2. Numerical data data conversion is important
3. Geo-location: may add important insights but additional package is required


### Exploring "vancouver_trees"
```{r}
### EXPLORE HERE ###
str(vancouver_trees)

#checking the species types
vancouver_trees %>% distinct(species_name)

#checking species type counts
vancouver_trees %>%  count(species_name, sort = TRUE)

```

**Comments**

1. Data has address in string
2. Too many categories in variables like species_name, genus_name
3. Geo-location: may add important insights but additional package is required


### Exploring "apt_buildings"
```{r}
### EXPLORE HERE ###
str(apt_buildings)

#checking the variables
apt_buildings %>% names()

#checking air conditioned units
apt_buildings %>%  count(air_conditioning, sort = TRUE)

```

**Comments**

1. Data has multiple types of variables to work with
2. Numerical data is present for analysis, requires faily less effort
3. Geo-location: data not present, which is a relief.
4. Binary and categorical data has good listings


### Exploring "building_permits"
```{r}
### EXPLORE HERE ###
str(building_permits)

#checking the variables
building_permits %>% names()

#checking year of buildings
building_permits %>%  count(year, sort = TRUE)

```

**Comments**

1. Data has multiple string entries
2. Multiple classes of data present: datetime, chr, num
3. Numerical data is only with year and project_value
4. Trying to avoid data with exact address as it may have privacy concern

<!----------------------------------------------------------------------------->



1.3 Now that you've explored the 4 datasets that you were initially most interested in, let's narrow it down to 2. What lead you to choose these 2? Briefly explain your choices below, and feel free to include any code in your explanation.

<!-------------------------- Start your work below ---------------------------->
### Choosing TWO dataset for analysis

Le us look at the variables by printing the summary. *summary()* is a generic function which prints the summary of different data types with statistics, missing data etc.

```{r}
summary(apt_buildings)
```

* *apt_buildings*:
  + This dataset contains combination of multiple types of dataset: Binary, Categorical and numerical
  + There are max 154 missing data (for the variable: no_barrier_free_accessible_units)
  + Research questions can be developed using the variables, such as Window_type, year_registered, air_conditioning etc.
  
```{r}
summary(vancouver_trees)
```


* *vancouver_trees*:
  + This dataset contains combination of multiple format of data: character, numeric, Date, Binary, Categorical
  + There are max 76548 missing data (for the variable: date_planted)
  + Research questions can be developed using the variables, such as genus_name, species_name, neighborhood_name etc.
  + String data can be complex to analyze and might require additional knowledge/time and resources to process. 
  
<!----------------------------------------------------------------------------->

1.4 Time for the final decision! Going back to the beginning, it's important to have an *end goal* in mind. For example, if I had chosen the `titanic` dataset for my project, I might've wanted to explore the relationship between survival and other variables. Try to think of 1 research question that you would want to answer with each dataset. Note them down below, and make your final choice based on what seems more interesting to you!

<!-------------------------- Start your work below ---------------------------->

### Defining End Goal:
Based on the data variables and types of available dataset, I finally choose to work with *apt_buildings* dataset. I want to explore the status of heating/cooling of Toronto Apartment Buildings and it's relationship with building type, structure and age.

**Broad Research Question:**

**How does Registered Toronto Apartments adopted the heating/cooling system for their livelihood?**

This question can be answered by analyzing the data from *apt_buildings* and choosing appropriate variables. 
<!----------------------------------------------------------------------------->


# Task 2: Exploration of dataset (15 points)

If we rewind and go back to the learning objectives, you'll see that by the end of this deliverable, you should have formulated *4* research questions about your data that you may want to answer during your project. However, it may be handy to do some more exploration on your dataset of choice before creating these questions - by looking at the data, you may get more ideas. **Before you start this task, read all instructions carefully until you reach START HERE under Task 3**.

2.1 Complete *4 out of the following 8 exercises* to dive deeper into your data. All datasets are different and therefore, not all of these tasks may make sense for your data - which is why you should only answer *4*. Use *dplyr* and *ggplot*.

1.  Plot the distribution of a numeric variable.
2.  Create a new variable based on other variables in your data (only if it makes sense)
3.  Investigate how many missing values there are per variable. Can you find a way to plot this?
4.  Explore the relationship between 2 variables in a plot.
5.  Filter observations in your data according to your own criteria. Think of what you'd like to explore - again, if this was the `titanic` dataset, I may want to narrow my search down to passengers born in a particular year...
6.  Use a boxplot to look at the frequency of different observations within a single variable. You can do this for more than one variable if you wish!
7.  Make a new tibble with a subset of your data, with variables and observations that you are interested in exploring.
8.  Use a density plot to explore any of your variables (that are suitable for this type of plot).

2.2 For each of the 4 exercises that you complete, provide a *brief explanation* of why you chose that exercise in relation to your data (in other words, why does it make sense to do that?), and sufficient comments for a reader to understand your reasoning and code.

**** 
<!-------------------------- Start your work below ---------------------------->

We are exploring the dataset *apt_buildings*.
First, I am listing out the variables in the main tibble from which I will choose the useful variables for further exploration and for framing 4 research questions. 

```{r}
names(apt_buildings)
```

Now looking at all the columns and possible data in the dataframe by glimpse() function.
```{r}
glimpse(apt_buildings)
```

Out of these variables, based on the overall research goal defined, I am considering the following variables:

1. **air_conditioning**: Does the building have an air conditioner? If so, is it central or in individual units? This is a *categorical* variable, which could have a major influence on the research question.
2. **year_built**: Year the building was built. This numerical data set can be converted into YEAR (time series) for analysing temporal trend in dataset.
3. **year_registered**: Year that the building was registered in the ABS (Apartment Building Registered) program. Some of the buildings and it's units can be old. However, I assume when the buildings were registered, they follow the bylaws of the local authority. Upon searching (Link: https://ckan0.cf.opendata.inter.prod-toronto.ca/tr/dataset/apartment-building-registration), I identified that buildings with 3 or more storeys and 10 or more units required registration. However, to avoid any bias in the results, the data needs to be verified in such contexts before performing any analysis.
4. **no_of_storeys**: Number of storeys in the building. Important criteria for getting idea about building's height, which might impact the heating/cooling system.
5. **no_of_units**: Number of units present in the building. This variable can profice information about the capacity of building. 
6. **heating_type**: How is the building heated? A categorical variable provides informations about the building heating information. 
7. **cooling_room**: Does the building have a cooling room? Provides information about the centralized amenities if there are no air-conditioning installed. 

#### Create an updated Dataset:
Using the variables considered (mentioned above), I am creating a subset of the main dataset which will be used for further analysis. This will reduce the tibble size and simplify the analysis. In addition to that, I am changing categorical data entries to *Factor* as it is easy to perform calculations, filtering data and visualization. NOTE: *str()* function is used to confirm the data types followed by data wrangling. 

```{r}
# select the required columns
sub_apt_buildings = apt_buildings %>% 
  select(id, air_conditioning, year_built, year_registered, no_of_storeys, no_of_units,
                                             heating_type, cooling_room) 

# check the structure of the tibble
str(sub_apt_buildings)

# factorize "Character" data
sub_apt_buildings = sub_apt_buildings %>% 
  mutate(air_conditioning = as.factor(air_conditioning),
         heating_type = as.factor(heating_type),
         cooling_room = as.factor(cooling_room))

# check the structure of the tibble AGAIN
str(sub_apt_buildings)
```

#### Visualizing Missing Data
To visualize the missing data, I am using a package **naniar**. This package provides simple (one line function for both calculation and visualization) calculations/estimations of missing data by variables and provides helpful visualizations on ggplot platform.

*What percentage of data missing by variable in **apt_building** tibble?*

```{r}
gg_miss_var(apt_buildings, show_pct = TRUE)
```

The above plot creates a visual analogue of the missing data (in %ge) with variables plotted in order of the missing data. Clearly, data with *amenities* consists of maximum percentage of missing data. Hoever, it does not affect out data analysis as this variable has been considered out of scope of the research question formed earlier.
Since, we have prepared a data subset, let us look at the missing data in **sub_apt_building**

```{r}
gg_miss_var(sub_apt_buildings, show_pct = TRUE)
```

To keep the data analysis **meaningful** for all the combinations of categories (heating, cooling, age etc.), I am dropping the missing data entries using *drop_na()* function from dplyr. This might include additional uncertainty in the results as some of the non-registered buildings might have been entries in different categories. Hence, following analysis will consider about the buildings which are registered under Toronto Building Authority. This will keep the analysis clean and meaningful for future policy relevant understandings.

#### Creating a new variable for analysis (removing all NA)
For the analysis, I am creating a new feature called "Decade" from the variable *year_built*. This will provide us about the understanding the time period of build development. Whether the buildings were developed in a particular period or if it follows a particular event in history. I am using a function *floor()* which returns the rounded down value to the nearest integer. 

```{r}
sub_apt_buildings = 
  sub_apt_buildings %>% 
  drop_na() %>% 
  mutate(Decade = floor(year_built/10)*10) # --> floor() 

```

#### Plotting the Decadal results of Building Developement:

Now let's visualize the number of buildings developed by each decade across the records. To visualize this, I am using a bar plot for the entries (counts) in each decade.
```{r}
sub_apt_buildings %>%
  ggplot(.,aes(x = Decade))+  
  geom_bar()+
  scale_y_continuous(trans='log10')+ # --> log transformation for better visualization
  labs(x = "Decade", y = "Count", title= "Number of Buildings Developed")+ # --> axis formatting
  theme_classic()+
  theme(axis.title.x = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        axis.title.y = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        plot.title = element_text(size=14, face="bold",hjust = 0.5)) # --> Title formating
```

This bar-plot shows the decade-wise building development in the Toronto area. I have log-transformed the count values (y-axis) for better visualization in the data. It is clear that some registered buildings are very old, built in decade 1800, followed by a huge gap of about 8 decades. For the sake of analysis, I am removing the old buildings by filtering (decade < 1880) data.

```{r}
filt_sub_apt_buildings = 
  sub_apt_buildings %>% filter(Decade>=1880) # --> keeping data from decade 1880
```

Now plotting again to have better visualization

```{r}
filt_sub_apt_buildings %>%
  ggplot(.,aes(x = Decade))+  
  geom_bar()+
  scale_y_continuous(trans='log10')+ # --> log transformation for better visualization
  labs(x = "Decade", y = "Count", title= "Number of Buildings Developed after 1880")+ # --> axis formatting
  theme_classic()+
  theme(axis.title.x = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        axis.title.y = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        plot.title = element_text(size=14, face="bold",hjust = 0.5)) # --> Title formating
```

To get the top three decades where most of the buildings were developed, I use the following code chunk. 

```{r}
filt_sub_apt_buildings %>% 
  count(Decade, sort = TRUE) %>% # sorting year based on the number of buildings built
  slice(1:3) %>%  # selecting the top three 
  kbl(align = "c", booktabs = T, 
      caption = "<center><strong>Top Three Decades</strong></center>") 

```


It is clear that, 1950 - 1970 was the peak period of construction. This boom in building development overlaps with the apartment bloom in 1960s. 

#### Analyzing Building's Age

First we have to know which year is the latest built-year as per the records 
```{r}
max(sub_apt_buildings$year_built)
```
The latest built is in the year **2019**

Hence, Age of Building (**building_age**) = 2019 - year_built

Creating a new numerical variable **building_age** from the records. 
```{r}
# calculating building_age
filt_sub_apt_buildings = filt_sub_apt_buildings %>% 
  mutate(building_age = 2019 - year_built)
```

Let us visualize the age distribution of the buildings using histogram.
```{r}
# Building Age Distribution
filt_sub_apt_buildings %>% 
  ggplot(.,aes(x = building_age))+
  geom_histogram(color="black", fill="blue")+ # --> formatting appearance
  labs(x = "Building Age (years)", y = "Count", title= "Age of Building Developed")+ # --> axis formatting
  theme_classic()+
  ylim(0,600)+
  theme(axis.title.x = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        axis.title.y = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        plot.title = element_text(size=14, face="bold",hjust = 0.5)) # --> Title formating

```

##### Heating System by building age:
To visualize the building age by the Heating type installed, I am using box plots to know the range of different categories.

```{r}
filt_sub_apt_buildings %>% 
  ggplot(.,aes(x = building_age, y = heating_type))+
  geom_boxplot()+
  labs(x = "Building Age (years)", y = "Heating Type", 
       title= "Boxplot of Building age by Heating Type")+ # --> axis formatting
  theme_classic()+
  theme(axis.title.x = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        axis.title.y = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        plot.title = element_text(size=14, face="bold",hjust = 0.5)) # --> Title formatting
```


##### Cooling System by building age:
How about the building age with installed air-conditioning facilities? Boxplots produced from the different categories.
```{r}
filt_sub_apt_buildings %>% 
  ggplot(.,aes(x = building_age, y = air_conditioning))+
  geom_boxplot()+
  labs(x = "Building Age (years)", y = "Air Conditioning Type", 
       title= "Boxplot of Building age by Air Conditioning Type")+ # --> axis formatting
  theme_classic()+
  theme(axis.title.x = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        axis.title.y = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        plot.title = element_text(size=14, face="bold",hjust = 0.5)) # --> Title formatting
```


##### Cooling-Room Availability by Building Age:
Does the cooling room availability ranged to different building age? Boxplots produced following previous procedure. 
```{r}
filt_sub_apt_buildings %>% 
  ggplot(.,aes(x = building_age, y = cooling_room))+
  geom_boxplot()+
  labs(x = "Building Age (years)", y = "Cooling Room", 
       title= "Boxplot of Building age by Cooling Room Availability")+ # --> axis formatting
  theme_classic()+
  theme(axis.title.x = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        axis.title.y = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        plot.title = element_text(size=14, face="bold",hjust = 0.5)) # --> Title formatting
```


<!----------------------------------------------------------------------------->

# Task 3: Write your research questions (5 points)

So far, you have chosen a dataset and gotten familiar with it through exploring the data. Now it's time to figure out 4 research questions that you would like to answer with your data! Write the 4 questions and any additional comments at the end of this deliverable. These questions are not necessarily set in stone - TAs will review them and give you feedback; therefore, you may choose to pursue them as they are for the rest of the project, or make modifications!


<!--- *****START HERE***** --->
### Research Questions
- Question 1: Does the heating system installed in the building related to the building age?
- Question 2: Does the air-conditioning system installed in the building related to the building age?
- Question 3: What type of buildings are tend to have cooling-room facility?
- Question 4: Is there any evidence of relationship in heating-cooling system in the registered buildings of Toronto?

- Additional Comments: These questions were formulated based on the previous data exploration and visualzations. 



# Task 4: Process and summarize your data (13 points)

From Task 2, you should have an idea of the basic structure of your dataset (e.g. number of rows and columns, class types, etc.). Here, we will start investigating your data more in-depth using various data manipulation functions.

### 1.1 (10 points)

Now, for each of your four research questions, choose one task from options 1-4 (summarizing), and one other task from 4-8 (graphing). You should have 2 tasks done for each research question (8 total). Make sure it makes sense to do them! (e.g. don't use a numerical variables for a task that needs a categorical variable.). Comment on why each task helps (or doesn't!) answer the corresponding research question.

Ensure that the output of each operation is printed!

**Summarizing:**

1.  Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data.


2.  Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!


3.  Create a categorical variable with 3 or more groups from an existing numerical variable. You can use this new variable in the other tasks! *An example: age in years into "child, teen, adult, senior".*


4.  Based on two categorical variables, calculate two summary statistics of your choosing.

**Graphing:**

5.  Create a graph out of summarized variables that has at least two geom layers.
6.  Create a graph of your choosing, make one of the axes logarithmic, and format the axes labels so that they are "pretty" or easier to read.
7.  Make a graph where it makes sense to customize the alpha transparency.
8.  Create 3 histograms out of summarized variables, with each histogram having different sized bins. Pick the "best" one and explain why it is the best.

Make sure it's clear what research question you are doing each operation for!

<!------------------------- Start your work below ----------------------------->
- Question 1: Does the heating system installed in the building related to the building age?
- Question 2: Does the air-conditioning system installed in the building related to the building age?
- Question 3: What type of buildings are tend to have cooling-room facility?
- Question 4: Is there any evidence of relationship in heating-cooling system in the registered buildings of Toronto?

#### Research Question 1: Does the heating system installed in the building related to the building age?

- summarizing data

```{r}
filt_sub_apt_buildings %>% 
  ungroup() %>% # --> ungrouping data 
  group_by(heating_type) %>% # --> grouping data 
  summarise(MeanAge = mean(building_age), ##--> calculating mean age of buildings
            MinAge = min(building_age), ##--> calculating Minimum age of buildings
            MaxAge = max(building_age), ##--> calculating Maximum age of buildings
            MedianAge = median(building_age)) ##--> calculating median age of buildings
```

- graphing 

```{r}
filt_sub_apt_buildings %>% 
  ggplot(.,aes(x = building_age, y = heating_type))+
  geom_boxplot()+
  labs(x = "Building Age (years)", y = "Cooling Room", 
       title= "Boxplot of Building age by Cooling Room Availability")+ # --> axis formatting
  theme_classic()+
  theme(axis.title.x = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        axis.title.y = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        plot.title = element_text(size=14, face="bold",hjust = 0.5)) # --> Title formatting
```

- comment

#### Research Question 2: Does the air-conditioning system installed in the building related to the building age?

- summarizing 


```{r}
filt_sub_apt_buildings %>% 
  ungroup() %>% # --> ungrouping data 
  group_by(air_conditioning) %>% # --> grouping data 
  summarise(MeanAge = mean(building_age), ##--> calculating mean age of buildings
            MinAge = min(building_age), ##--> calculating Minimum age of buildings
            MaxAge = max(building_age), ##--> calculating Maximum age of buildings
            MedianAge = median(building_age)) ##--> calculating median age of buildings
```
- graphing 

```{r}

filt_sub_apt_buildings %>% 
  ggplot(.,aes(x = building_age, y = air_conditioning))+
  geom_boxplot()+
  labs(x = "Building Age (years)", y = "Cooling Room", 
       title= "Boxplot of Building age by Cooling Room Availability")+ # --> axis formatting
  theme_classic()+
  theme(axis.title.x = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        axis.title.y = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        plot.title = element_text(size=14, face="bold",hjust = 0.5)) # --> Title formatting
```



- comment

#### Research Question 3: What type of buildings are tend to have cooling-room facility?
- summarizing 

```{r}
filt_sub_apt_buildings %>% 
  ungroup() %>% # --> ungrouping data 
  group_by(cooling_room) %>% # --> grouping data 
  summarise(MeanAge = mean(building_age), ##--> calculating mean age of buildings
            MinAge = min(building_age), ##--> calculating Minimum age of buildings
            MaxAge = max(building_age), ##--> calculating Maximum age of buildings
            MedianAge = median(building_age)) ##--> calculating median age of buildings
```
- graphing 

```{r}

filt_sub_apt_buildings %>% 
  ggplot(.,aes(x = building_age, y = cooling_room))+
  geom_boxplot()+
  labs(x = "Building Age (years)", y = "Cooling Room", 
       title= "Boxplot of Building age by Cooling Room Availability")+ # --> axis formatting
  theme_classic()+
  theme(axis.title.x = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        axis.title.y = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        plot.title = element_text(size=14, face="bold",hjust = 0.5)) # --> Title formatting
```


- comment


#### Research Question 4:
- summarizing 
- graphing 
- comment

```{r}
names(apt_buildings)

```


```{r}

apt_buildings %>% group_by(air_conditioning) %>% 
  summarize(n = n())

apt_buildings %>% group_by(no_of_storeys) %>% 
  summarize(n = n()) %>% 
  ggplot(.,aes(x = no_of_storeys, y = n))+
  geom_bar(stat = "identity")

apt_buildings %>% group_by(year_built) %>% 
  summarise(n = n()) %>% 
  ggplot(.,aes(x = year_built, y = n))+
  geom_bar(stat = "identity")

apt_buildings %>% group_by(year_registered) %>% 
  summarise(n = n()) %>% 
  ggplot(.,aes(x = year_registered, y = n))+
  geom_bar(stat = "identity")

apt_buildings %>% group_by(heating_type) %>% 
  summarise(n = n()) %>% 
  ggplot(.,aes(x = heating_type, y = n))+
  geom_bar(stat = "identity")

apt_buildings %>% group_by(laundry_room) %>% 
  summarise(n = n()) %>% 
  ggplot(.,aes(x = laundry_room, y = n))+
  geom_bar(stat = "identity")

apt_buildings %>% group_by(property_type) %>% 
  summarise(n = n()) %>% 
  ggplot(.,aes(x = property_type, y = n))+
  geom_bar(stat = "identity")

```



<!----------------------------------------------------------------------------->

### 1.2 (3 points)

Based on the operations that you've completed, how much closer are you to answering your research questions? Think about what aspects of your research questions remain unclear. Can your research questions be refined, now that you've investigated your data a bit more? Which research questions are yielding interesting results?

<!-------------------------- Start your work below ---------------------------->

<!----------------------------------------------------------------------------->

### Attribution

Thanks to Icíar Fernández Boyano for mostly putting this together, and Vincenzo Coia for launching.
