---
title: "Mini Data Analysis Milestone 2"
output: github_document
always_allow_html: yes
---

# Welcome to your second (and last) milestone in your mini data analysis project!

In Milestone 1, you explored your data, came up with research questions, and obtained some results by making summary tables and graphs. This time, we will first explore more in depth the concept of *tidy data.* Then, you'll be sharpening some of the results you obtained from your previous milestone by:

-   Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

**NOTE**: The main purpose of the mini data analysis is to integrate what you learn in class in an analysis. Although each milestone provides a framework for you to conduct your analysis, it's possible that you might find the instructions too rigid for your data set. If this is the case, you may deviate from the instructions -- just make sure you're demonstrating a wide range of tools and techniques taught in this class.

# Instructions

**To complete this milestone**, edit [this very `.Rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-2.Rmd) directly. Fill in the sections that are tagged with `<!--- start your work here--->`.

**To submit this milestone**, make sure to knit this `.Rmd` file to an `.md` file by changing the YAML output settings from `output: html_document` to `output: github_document`. Commit and push all of your work to your mini-analysis GitHub repository, and tag a release on GitHub. Then, submit a link to your tagged release on canvas.

**Points**: This milestone is worth 55 points (compared to the 45 points of the Milestone 1): 45 for your analysis, and 10 for your entire mini-analysis GitHub repository. Details follow.

**Research Questions**: In Milestone 1, you chose two research questions to focus on. Wherever realistic, your work in this milestone should relate to these research questions whenever we ask for justification behind your work. In the case that some tasks in this milestone don't align well with one of your research questions, feel free to discuss your results in the context of a different research question.

# Learning Objectives

By the end of this milestone, you should:

-   Understand what *tidy* data is, and how to create it using `tidyr`.
-   Generate a reproducible and clear report using R Markdown.
-   Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

# Setup

Begin by loading your data and the tidyverse package below:

```{r, message = FALSE}
library(datateachr) # <- might contain the data you picked!
library(tidyverse)

# additional libraries
library(ggpubr)
library(scales)
library(broom)
library(here)
```

# Task 1: Tidy your data (15 points)

In this task, we will do several exercises to reshape our data. The goal here is to understand how to do this reshaping with the `tidyr` package.

A reminder of the definition of *tidy* data:

-   Each row is an **observation**
-   Each column is a **variable**
-   Each cell is a **value**

*Tidy'ing* data is sometimes necessary because it can simplify computation. Other times it can be nice to organize data so that it can be easier to understand when read manually.

### 2.1 (2.5 points)

Based on the definition above, can you identify if your data is tidy or untidy? Go through all your columns, or if you have \>8 variables, just pick 8, and explain whether the data is untidy or tidy.

<!--------------------------- Start your work below --------------------------->

In the MDA deliverable #1, I chose to work with *apt_buildings*. In my previous analysis, I choose to work with 8 variables for the reserach question I have developed. Let's quickly check how the original data looked like.

```{r}
# checking the structure of dataframe
str(apt_buildings)
```

Out of the 37 variables in *apt_buildings*, I choose the following variables.

1.  **air_conditioning**: Does the building have an air conditioner? If so, is it central or in individual units? This is a *categorical* variable, which could have a major influence on the research question.
2.  **year_built**: Year the building was built. This numerical data set can be converted into YEAR (time series) for analysing temporal trend in dataset.
3.  **year_registered**: Year that the building was registered in the ABS (Apartment Building Registered) program. Some of the buildings and it's units can be old. However, I assume when the buildings were registered, they follow the bylaws of the local authority. Upon searching (Link: <https://ckan0.cf.opendata.inter.prod-toronto.ca/tr/dataset/apartment-building-registration>), I identified that buildings with 3 or more storeys and 10 or more units required registration. However, to avoid any bias in the results, the data needs to be verified in such contexts before performing any analysis.
4.  **no_of_storeys**: Number of storeys in the building. Important criteria for getting idea about building's height, which might impact the heating/cooling system.
5.  **no_of_units**: Number of units present in the building. This variable can profice information about the capacity of building.
6.  **heating_type**: How is the building heated? A categorical variable provides informations about the building heating information.
7.  **cooling_room**: Does the building have a cooling room? Provides information about the centralized amenities if there are no air-conditioning installed.

#### Creating an updated dataset

```{r}
# select the required columns
sub_apt_buildings = apt_buildings %>% 
  select(id, air_conditioning, year_built, year_registered, no_of_storeys, no_of_units,
                                             heating_type, cooling_room) 

# check the structure of the tibble
str(sub_apt_buildings)
```

From here, I will continue to work with *sub_apt_buildings* dataframe.

#### tidy data check

First, I check the summary of the tibble.

```{r}
sub_apt_buildings %>% 
  summary()
```

**Comments**

1.  Column headers are variable names, not values :white_check_mark:
2.  Columns "id", "year_built","year_registered","no_of_storeys","no_of_units" are numeric :white_check_mark:
3.  Columns "air_conditioning","heating_type" and "cooling_room" are character variables :white_check_mark:
4.  Is *sub_apt_buildings* a tidy data?
  - Each row is an **observation** :white_check_mark:
  - Each column is a **variable** :white_check_mark:
  - Each cell is a **value** :white_check_mark:
  - Conclusion: **YES**

<!----------------------------------------------------------------------------->

### 2.2 (5 points)

Now, if your data is tidy, untidy it! Then, tidy it back to it's original state.

If your data is untidy, then tidy it! Then, untidy it back to it's original state.

Be sure to explain your reasoning for this task. Show us the "before" and "after".

<!--------------------------- Start your work below --------------------------->

#### Undidying *sub_apt_buildings*

The concept of tidy data can change based on the objective of data analysis. The difference in messy and tidy can vary based on 
 - the objectives or goals of data usage (e.g., if we are to look at the relation of heating system installed only, we would prepare data based on heating types)
 - the tools or packages (*dplyr* and *ggplot2*) which will be used for analysis and visualization (e.g., in what form the variable of interest are, if variables can be used to group, select or summarize data)
 
A classic example of *sub_apt_buildings* untidy/messy data will be when we have individual year as columns.
```{r}
untidy_sub_apt_buildings = 
  sub_apt_buildings %>% 
  drop_na() %>%  ##-> dropping NA values
  pivot_wider(names_from = year_registered, 
              names_prefix = "heating_",
              values_from = heating_type)

head(untidy_sub_apt_buildings)

```

We can call *untidy_sub_apt_buildings* untidy because the data frame consists year of registration as columns, as in each year c(2017, 2018, 2019, 2020) are variables. This was achieved by widening the original data by a variable *year_registered*. This data set may not be useful for data filtering and summarizing when considering multi-variate analysis. However, this dataset could be useful when someone is only interested in looking at buildings registered in 2017. I am saying is in-terms of ease of data handling. With thousands of data, it might be better to consider widening data and look at a particular for analysis. However, this is not the case in the present context. 

#### Re-tidying the Undidy data

```{r}
untidy_sub_apt_buildings %>% 
  pivot_longer(cols = c("heating_2017","heating_2018","heating_2019","heating_2020"),
               names_to = c(".value","year_registration"),
               names_sep = "_") %>% 
  head()

```


<!----------------------------------------------------------------------------->

### 2.3 (7.5 points)

Now, you should be more familiar with your data, and also have made progress in answering your research questions. Based on your interest, and your analyses, pick 2 of the 4 research questions to continue your analysis in the next four tasks:

<!-------------------------- Start your work below ---------------------------->

In MDA#1, I had developed four research questions

- Question 1: Does the heating system installed in the building related to the building age?
- Question 2: Does the air-conditioning system installed in the building related to the building age?
- Question 3: What type of buildings are tend to have cooling-room facility?
- Question 4: Is there any evidence of relationship in heating-cooling system in the registered buildings of Toronto?

From the research question, I am trying to identify two questions which are relevant for further tasks and analysis.

1.  *Does the heating system installed in the building related to the building age*
2.  *Is there any evidence of relationship in heating-cooling system in the registered buildings of Toronto*
o
<!----------------------------------------------------------------------------->

Explain your decision for choosing the above two research questions.

<!--------------------------- Start your work below --------------------------->

These questions will help us understand the relationship of building heating/cooling facility. The building data set is very complex has lots of biases in terms of temporal evolution of buildings types and their installation of heating/cooling facility. It will be interesting to check if there are any association within types of building and the heating/cooling facility. Here, I will explain the rationale behind the different categories. 

<!----------------------------------------------------------------------------->

Now, try to choose a version of your data that you think will be appropriate to answer these 2 questions. Use between 4 and 8 functions that we've covered so far (i.e. by filtering, cleaning, tidy'ing, dropping irrelevant columns, etc.).

<!--------------------------- Start your work below --------------------------->

#### Data Processing
Firstly, I am creating new data columns for analysis which is often mentioned as creating new features in the data set for data analysis. 

##### Create: Decade
The variable "Decade" refers to the decade, in which data building was built. Note: I am dropping all NA entries for data uniformity. 

```{r}
sub_apt_buildings = 
  sub_apt_buildings %>% 
  drop_na() %>% 
  mutate(Decade = floor(year_built/10)*10) # --> floor() 
```

In MDA#1, I have shown that there are few entries for Decade<1880. This is how we can visualize.

```{r}
sub_apt_buildings %>%
  ggplot(.,aes(x = Decade))+  
  geom_bar()+
  scale_y_continuous(trans='log10')+ # --> log transformation for better visualization
  labs(x = "Decade", y = "Count", title= "Number of Buildings Developed")+ # --> axis formatting
  theme_classic()+
  theme(axis.title.x = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        axis.title.y = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        plot.title = element_text(size=14, face="bold",hjust = 0.5)) # --> Title formating
```
Hence, we are filtering data for Decade<1800

```{r}
filt_sub_apt_buildings = 
  sub_apt_buildings %>% filter(Decade>=1880) # --> keeping data from decade 1880
```

Now plotting again to have better visualization

```{r}
filt_sub_apt_buildings %>%
  ggplot(.,aes(x = Decade))+  
  geom_bar()+
  scale_y_continuous(trans='log10')+ # --> log transformation for better visualization
  labs(x = "Decade", y = "Count", title= "Number of Buildings Developed after 1880")+ # --> axis formatting
  theme_classic()+
  theme(axis.title.x = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        axis.title.y = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        plot.title = element_text(size=14, face="bold",hjust = 0.5)) # --> Title formating
```
##### Create : building_age

Creating a new numerical variable **building_age** from the records. 
```{r}
# calculating building_age
filt_sub_apt_buildings = filt_sub_apt_buildings %>% 
  mutate(building_age = 2019 - year_built)
```

Let us visualize the age distribution of the buildings using histogram.
```{r}
# Building Age Distribution
filt_sub_apt_buildings %>% 
  ggplot(.,aes(x = building_age))+
  geom_histogram(color="black", fill="blue")+ # --> formatting appearance
  labs(x = "Building Age (years)", y = "Count", title= "Age of Building Developed")+ # --> axis formatting
  theme_classic()+
  ylim(0,600)+
  theme(axis.title.x = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        axis.title.y = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        plot.title = element_text(size=14, face="bold",hjust = 0.5)) # --> Title formatting

```

##### Create : building_class
I am crating a new categorical variable based on building's number of storeys. The facilities in the building can be related to the building storeys which are often manages by property managers and are often heating/cooling facilities are well taken care of. The building classification has been adopted from this study: https://www.mdpi.com/2071-1050/11/20/5663 

```{r}
filt_sub_apt_buildings = filt_sub_apt_buildings %>% 
  mutate(building_class = case_when(no_of_storeys <=3 ~ "Low-Rise",
                                    no_of_storeys <=6 ~ "Multi-Story",
                                    no_of_storeys <=9 ~ "Middle-Rise",
                                    no_of_storeys <=16 ~ "Small_High-Rise",
                                    no_of_storeys <=40 ~ "High-Rise",
                                    TRUE ~ "Ultra_High-Rise"))

```

Now checking the count of different classes of building

```{r}
filt_sub_apt_buildings %>% group_by(building_class) %>% 
  summarize(Count = n())
```

##### Outlier Removal:

```{r}
filt_sub_apt_buildings %>% 
  ggplot(.,aes(x = no_of_units, y = building_class))+
  geom_boxplot()

```
Clearly, there is one entry in High-Rise category building which has more than 4000 units and hence can be considered as outlier entry.By the above visualization, I am considering a filter on no_of_units <1000 and creating a new tibble. 

```{r}
out_filt_sub_apt_buildings = filt_sub_apt_buildings %>% 
  filter(no_of_units<1000) 

out_filt_sub_apt_buildings %>% 
  ggplot(.,aes(x = no_of_units, y = building_class))+
  geom_boxplot()
  
```
Now outlier data entry has been removed. 

##### Final Dataset
```{r}
# Make Character Variables as Factor

out_filt_sub_apt_buildings = 
  out_filt_sub_apt_buildings %>% 
  mutate(air_conditioning = as.factor(air_conditioning),
         heating_type = as.factor(heating_type),
         cooling_room = as.factor(cooling_room),
         building_class = as.factor(building_class))

#Check the structure of the final data
str(out_filt_sub_apt_buildings)
```

<!----------------------------------------------------------------------------->

# Task 2: Special Data Types (10)

For this exercise, you'll be choosing two of the three tasks below -- both tasks that you choose are worth 5 points each.

But first, tasks 1 and 2 below ask you to modify a plot you made in a previous milestone. The plot you choose should involve plotting across at least three groups (whether by facetting, or using an aesthetic like colour). Place this plot below (you're allowed to modify the plot if you'd like). If you don't have such a plot, you'll need to make one. Place the code for your plot below.

<!-------------------------- Start your work below ---------------------------->

##### The Plot
```{r}

out_filt_sub_apt_buildings %>% 
  ggplot(.,aes(x = building_class, y = building_age))+
  geom_boxplot()

```

<!----------------------------------------------------------------------------->

Now, choose two of the following tasks.

1.  Produce a new plot that reorders a factor in your original plot, using the `forcats` package (3 points). Then, in a sentence or two, briefly explain why you chose this ordering (1 point here for demonstrating understanding of the reordering, and 1 point for demonstrating some justification for the reordering, which could be subtle or speculative.)

2.  Produce a new plot that groups some factor levels together into an "other" category (or something similar), using the `forcats` package (3 points). Then, in a sentence or two, briefly explain why you chose this grouping (1 point here for demonstrating understanding of the grouping, and 1 point for demonstrating some justification for the grouping, which could be subtle or speculative.)


<!-------------------------- Start your work below ---------------------------->

**Task Number**: 1

```{r}
out_filt_sub_apt_buildings %>% 
  ggplot(.,aes(x = building_class, y = building_age))+
  geom_boxplot()
```
From the above plot, it is difficult to understand the building classes and their age. As the factor variable, building_class is in reality a ordinal variable, representing building size from low to high (based on number of storeys), this visualization does not provide an ordinal representation. Hence, the building class needs to be re-leveled using forecats package. However, this processing could be avoided if we mentioned the levels while creating the variable using case_when() function.

```{r}

out_filt_sub_apt_buildings %>% 
  mutate(building_class = fct_relevel(building_class, "Low-Rise","Multi-Story","Middle-Rise",
                                     "Small_High-Rise","High-Rise","Ultra_High-Rise")) %>% 
  ggplot(.,aes(x = building_age, y = building_class))+
  geom_boxplot()+
  labs(x = "Building Age (years)", y = "Building Classsification", 
       title= "Boxplot of Building age and Class by Cooling Room Availability")+ # --> axis formatting
  theme_pubr()+
  theme(axis.title.x = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        axis.title.y = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        plot.title = element_text(size=14, face="bold",hjust = 0.5)) # --> Title formatting


```
Here, it is clearly visible that the building class is ordered based on the building height, which is helpful to interpret. 

<!----------------------------------------------------------------------------->

<!-------------------------- Start your work below ---------------------------->

**Task Number**: 2

2.  Produce a new plot that groups some factor levels together into an "other" category (or something similar), using the `forcats` package (3 points). Then, in a sentence or two, briefly explain why you chose this grouping (1 point here for demonstrating understanding of the grouping, and 1 point for demonstrating some justification for the grouping, which could be subtle or speculative.)

In this task, I am defining a new factor group *building_class2* which is grouped by three types of building. 
 - Low-Rise : by combining "Low_Rise" and "Multi-Story"
 - Medium-Rise: building which are previously classified as "Middle-Rise".
 - High-Rise: by combining "Small High-Rise","High-Rise", and "Ultra High-Rise"

```{r}

out_filt_sub_apt_buildings$building_class2 = 
  fct_collapse(out_filt_sub_apt_buildings$building_class,
    "Low-Rise" = c("Low_Rise","Multi-Story"),
    "Medium-Rise" = c("Middle-Rise"),
    "High-Rise" = c("Small_High-Rise","High-Rise","Ultra_High-Rise"))


# Plotting
out_filt_sub_apt_buildings %>% 
  mutate(building_class2 = fct_relevel(building_class2, "Low-Rise","Medium-Rise","High-Rise")) %>% 
  ggplot(.,aes(x = building_age, y = building_class2))+
  geom_boxplot()+
  labs(x = "Building Age (years)", y = "Building Classification 2", 
       title= "Boxplot of Building age and Class by Cooling Room Availability")+ # --> axis formatting
  theme_pubr()+
  theme(axis.title.x = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        axis.title.y = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        plot.title = element_text(size=14, face="bold",hjust = 0.5)) # --> Title formatting
```

This new classification was done to reflect simple groups in building types. Earlier there were three types of building in High-Rise category. Where number of observations in Ultra_High-Rise building classification were very less. Combining to new Building Classification #2, the groups are clear and intuitive for understanding.

Another way visualizing the importance of grouping could be from percentage of a different categorical varaible (e.g., heating type) in each building class. 
```{r}
out_filt_sub_apt_buildings %>% 
  group_by(building_class,heating_type) %>% 
  summarise(count = n()) %>% 
  ggplot(.,aes(fill = heating_type, y = count, x = building_class))+
  geom_bar(position = "fill", stat = "identity")+
  scale_y_continuous(labels = scales::percent)+
  labs(x = "Building Classification", y = "Percentage (%)", 
       title= "Share of Heating Type installed in Different Types of Building")+ # --> axis formatting
  theme_pubr()+
  theme(axis.title.x = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        axis.title.y = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        plot.title = element_text(size=14, face="bold",hjust = 0.5), # --> Title formatting
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) # --> Rorate axis labels


```

It is clearly visible that the "Ultra_High-Rise" building doesn't have all the Heating Type categories present. Sometimes, re-grouping factors can help us visualize this as shown below

```{r}

# implement factor releveling
out_filt_sub_apt_buildings = out_filt_sub_apt_buildings %>% 
  mutate(building_class2 = fct_relevel(building_class2, "Low-Rise","Medium-Rise","High-Rise"))

# plot data
out_filt_sub_apt_buildings %>% 
  group_by(building_class2,heating_type) %>% 
  summarise(count = n()) %>% 
  ggplot(.,aes(fill = heating_type, y = count, x = building_class2))+
  geom_bar(position = "fill", stat = "identity")+
  scale_y_continuous(labels = scales::percent)+
  labs(x = "Building Classification 2", y = "Percentage (%)", 
       title= "Share of Heating Type installed in Different Types of Building")+ # --> axis formatting
  theme_pubr()+
  theme(axis.title.x = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        axis.title.y = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        plot.title = element_text(size=14, face="bold",hjust = 0.5), # --> Title formatting
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) # --> Rorate axis labels
```

<!----------------------------------------------------------------------------->

# Task 3: Modelling

## 2.0 (no points)

Pick a research question, and pick a variable of interest (we'll call it "Y") that's relevant to the research question. Indicate these.

<!-------------------------- Start your work below ---------------------------->

**Research Question**: 
Are there any relationship among the heating type and air conditioning type present in the buildings based on building category (building_class2)? 

Note: The development of this question has been based on assumption that factored variables of interest are random variables

**Variable of interest**: building_class2

<!----------------------------------------------------------------------------->

## 2.1 (5 points)

Fit a model or run a hypothesis test that provides insight on this variable with respect to the research question. Store the model object as a variable, and print its output to screen. We'll omit having to justify your choice, because we don't expect you to know about model specifics in STAT 545.

<!-------------------------- Start your work below ---------------------------->

If we look at the structure of the dataset *out_filt_sub_apt_buildings*, we can identify several variables has factored levels, which are of our core interest. Even though the categorical variable *building_class2* can be identified as ordered variable based on height, for the purpose of analysis, I am considering them as unordered. To understand if there is correlation among the levels of categorical variables, **significance test** and **effect size (strength of association)** can be used. Now, I am going to apply chi-squared test of independence to measure if the dependency is significant or not. 

##### Examining relaionship between Building Class and Heating Type

Assuming the variables *building_class2* and *heating_type* as random variables, the chi-squared test of independence can provide information whether or not there exists a statistical dependence. 

 - **Null Hypothesis, H0** = building_class2 and heating_type are *independent*
 - **Alternative Hypothesis, H1** = building_class2 and heating_type are *dependent*
 
```{r}

chi_building_heating = chisq.test(out_filt_sub_apt_buildings$building_class2,out_filt_sub_apt_buildings$heating_type, correct = FALSE)

print(chi_building_heating)

```
Since, the p-value is **0.01093** is less than the cut-off value of 0.05, we can reject the null-hypothesis in favor of alternative hypothesis and conclude, that the variables, *building_class2* and *heating_type* are **dependent to each other**. 


##### Examining relaionship between Building Class and Air Conditioning

Assuming the variables *building_class2* and *air_conditioning* as random variables, the chi-squared test of independence can provide information whether or not there exists a statistical dependence. 

 - **Null Hypothesis, H0** = building_class2 and air_conditioning are *independent*
 - **Alternative Hypothesis, H1** = building_class2 and air_conditioning are *dependent*
 

```{r}

chi_building_aircond = chisq.test(out_filt_sub_apt_buildings$building_class2,out_filt_sub_apt_buildings$air_conditioning, correct = FALSE)

print(chi_building_aircond)
```
Since, the p-value is **<2.2e-16** is less than the cut-off value of 0.05, we can reject the null-hypothesis in favor of alternative hypothesis and conclude, that the variables, *building_class2* and *air_conditioning* are **dependent to each other**. 




<!----------------------------------------------------------------------------->

## 2.2 (5 points)

Produce something relevant from your fitted model: either predictions on Y, or a single value like a regression coefficient or a p-value.

-   Be sure to indicate in writing what you chose to produce.
-   Your code should either output a tibble (in which case you should indicate the column that contains the thing you're looking for), or the thing you're looking for itself.
-   Obtain your results using the `broom` package if possible. If your model is not compatible with the broom function you're needing, then you can obtain your results by some other means, but first indicate which broom function is not compatible.

<!-------------------------- Start your work below ---------------------------->

##### Checking if heating_type and air_conditioning are realted:
Earlier, I have showed that both *heating_type* and *air_conditioning* are dependent on *building_class2*. Now, it might be useful to assess if there any interdependence among these variables. Again, using chi-square test for the evaluation. 

 - **Null Hypothesis, H0** = heating_type and air_conditioning are *independent*
 - **Alternative Hypothesis, H1** = heating_type and air_conditioning are *dependent*
 

```{r}
chi_heating_aircond = chisq.test(out_filt_sub_apt_buildings$heating_type,out_filt_sub_apt_buildings$air_conditioning, correct = FALSE)

print(chi_heating_aircond)
```
Since, the p-value is **<2.2e-16** is less than the cut-off value of 0.05, we can reject the null-hypothesis in favor of alternative hypothesis and conclude, that the variables, *heating_type* and *air_conditioning* are **dependent to each other**. 

##### Futher Analysis on the categories of data:

Let's check the percentage of households with respect to time (here Decade) and see the evoloution of air-conditioning usage. 
```{r}
out_filt_sub_apt_buildings %>% 
  group_by(Decade, building_class2, air_conditioning) %>% 
  summarize(count = n()) %>% 
  ggplot(.,aes(fill = air_conditioning, y = count, x = Decade))+
  geom_bar(position = "fill", stat = "identity")+
  scale_y_continuous(labels = scales::percent)+
  facet_wrap(~building_class2, ncol=1)+
  labs(x = "Decade", y = "Percentage (%)", 
       title= "Share of Air Conditioning Type in Different Types of Building")+ # --> axis formatting
  theme_bw()+
  theme(axis.title.x = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        axis.title.y = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        plot.title = element_text(size=14, face="bold",hjust = 0.5), # --> Title formatting
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) # --> Rorate axis labels
```
As shown previously from the chi-square test, the dependency in building_type and air conditioning is visible. However, post 1950, the changes are much more prominent. (See above plot). This provides more information of further grouping data post 1950, where a proper relationship can be established. New nu,erical variables, such as percentage change over time can be created and used for this kind analysis.


```{r}
out_filt_sub_apt_buildings %>% 
  group_by(Decade, building_class2, heating_type) %>% 
  summarize(count = n()) %>% 
  ggplot(.,aes(fill = heating_type, y = count, x = Decade))+
  geom_bar(position = "fill", stat = "identity")+
  scale_y_continuous(labels = scales::percent)+
  facet_wrap(~building_class2, ncol=1)+
  labs(x = "Decade", y = "Percentage (%)", 
       title= "Share of Heating Type in Different Types of Building")+ # --> axis formatting
  theme_bw()+
  theme(axis.title.x = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        axis.title.y = element_text(color="Black", size=12, face="bold"), # --> axis formatting
        plot.title = element_text(size=14, face="bold",hjust = 0.5), # --> Title formatting
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) # --> Rorate axis labels
```
Same commentary as above. We see a decreasing trend of hot-water based heating system. 

**Newly built buildings tend to eliminate hot-water heating system and install central air conditioning system, as they might be energy efficient and reliable for better thermal comfort of the dwellers.**

<!----------------------------------------------------------------------------->

# Task 4: Reading and writing data

Get set up for this exercise by making a folder called `output` in the top level of your project folder / repository. You'll be saving things there.

## 3.1 (5 points)

Take a summary table that you made from Milestone 1 (Task 4.2), and write it as a csv file in your `output` folder. Use the `here::here()` function.

-   **Robustness criteria**: You should be able to move your Mini Project repository / project folder to some other location on your computer, or move this very Rmd file to another location within your project repository / folder, and your code should still work.
-   **Reproducibility criteria**: You should be able to delete the csv file, and remake it simply by knitting this Rmd file.

<!-------------------------- Start your work below ---------------------------->

##### First Check Function here::here()
```{r}
here()
```
This is the current location in my computer. 

##### Create a output folder:

```{r}
dir.create(here::here("output"))
```


##### Save Data from Milestone#1

```{r}
summary_data = 
  filt_sub_apt_buildings %>% 
  ungroup() %>% # --> ungrouping data 
  group_by(heating_type) %>% # --> grouping data 
  summarise(MeanAge = mean(building_age), ##--> calculating mean age of buildings
            MinAge = min(building_age), ##--> calculating Minimum age of buildings
            MaxAge = max(building_age), ##--> calculating Maximum age of buildings
            MedianAge = median(building_age)) ##--> calculating median age of buildings

# Saving csv file:
write_csv(summary_data, here::here("output", "summary_data.csv"))

```

<!----------------------------------------------------------------------------->

## 3.2 (5 points)

Write your model object from Task 3 to an R binary file (an RDS), and load it again. Be sure to save the binary file in your `output` folder. Use the functions `saveRDS()` and `readRDS()`.

-   The same robustness and reproducibility criteria as in 3.1 apply here.

<!-------------------------- Start your work below ---------------------------->

```{r}
# First combining the three chi-square outputs
model_object = c(chi_building_aircond, chi_building_heating, chi_heating_aircond)

# Saving RDS file:
saveRDS(model_object, here::here("output","model_object.rds"))

# Reading the RDS file
read_file = readRDS(here::here("output","model_object.rds"))
```

<!----------------------------------------------------------------------------->

# Tidy Repository

Now that this is your last milestone, your entire project repository should be organized. Here are the criteria we're looking for.

## Main README (3 points)

There should be a file named `README.md` at the top level of your repository. Its contents should automatically appear when you visit the repository on GitHub.

Minimum contents of the README file:

-   In a sentence or two, explains what this repository is, so that future-you or someone else stumbling on your repository can be oriented to the repository.
-   In a sentence or two (or more??), briefly explains how to engage with the repository. You can assume the person reading knows the material from STAT 545A. Basically, if a visitor to your repository wants to explore your project, what should they know?

Once you get in the habit of making README files, and seeing more README files in other projects, you'll wonder how you ever got by without them! They are tremendously helpful.

## File and Folder structure (3 points)

You should have at least three folders in the top level of your repository: one for each milestone, and one output folder. If there are any other folders, these are explained in the main README.

Each milestone document is contained in its respective folder, and nowhere else.

Every level-1 folder (that is, the ones stored in the top level, like "Milestone1" and "output") has a `README` file, explaining in a sentence or two what is in the folder, in plain language (it's enough to say something like "This folder contains the source for Milestone 1").

## Output (2 points)

All output is recent and relevant:

-   All Rmd files have been `knit`ted to their output, and all data files saved from Task 4 above appear in the `output` folder.
-   All of these output files are up-to-date -- that is, they haven't fallen behind after the source (Rmd) files have been updated.
-   There should be no relic output files. For example, if you were knitting an Rmd to html, but then changed the output to be only a markdown file, then the html file is a relic and should be deleted.

Our recommendation: delete all output files, and re-knit each milestone's Rmd file, so that everything is up to date and relevant.

PS: there's a way where you can run all project code using a single command, instead of clicking "knit" three times. More on this in STAT 545B!

## Error-free code (1 point)

This Milestone 1 document knits error-free, and the Milestone 2 document knits error-free.

Plots failing to show up on Github in the .md counts as an error here. So does the entire .md failing to show up on Github in the .md ("Sorry about that, but we can't show files that are this big right now").

## Tagged release (1 point)

You've tagged a release for Milestone 1, and you've tagged a release for Milestone 2.

### Attribution

Thanks to Victor Yuan for mostly putting this together.
